### 2017-04-26 thesis/latex/thesis.tex
Add y-trajectory plot.

More detailed stepping information is shown in Figure \ref{fig:stepping-trajectory}. The model steps both forwards and backwards, but has a definite forward bias.

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-trajectory}
  \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-trajectory}
\end{figure}

--------------------------
Histograms of the simulation's stepping length and time are shown in Figure \ref{fig:final-histograms}. This figure also shows histograms for experimental dynein stepping behavior.\\

@@

@@

@@

\section{Conclusion}
Does anything actually go here?

>>>>

More detailed stepping information is shown in Figure \ref{fig:stepping-x-trajectory}.a. The model steps both forwards and backwards, but has a definite forward bias. The model's behavior can be contrasted with experimental behavior in Figure \ref{fig:stepping-trajectory}.b. The two trajectory plots look very different, but share major key features: forwards and backwards steps, a directional bias, and varying step sizes. At a minimum, the two-state stepping model

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-x-trajectory}
  \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-x-trajectory}
\end{figure}

\subsection{Model steps reasonably}

@@

\subsection{Model does not drag as it steps}
The model lifts its foot up and lowers it as it is about to step; it doesn't drag along the microtubule searching for the binding site. This behavior is shown in Figure \ref{fig:stepping-y-trajectory}.\\

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-y-trajectory}
  \caption{Unbound binding domain position over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-y-trajectory}
\end{figure}

@@

\section{Conclusion}

@@
